Investigating Interventions

### 2023-03-01 minos/validation/interventions.Rmd
Added plots assessing the how the pathways react to the energy downlift intervention

require(tidyverse)
require(ggplot2)
require(purrr)

@@

@@

@@

@@

>>>>

require(tidyverse)
require(ggplot2)
require(purrr)
require(ordinal)
require(nnet)
require(pscl)

@@

## Transition Models

```{r, include=FALSE}
trans.path <- 'Minos/data/transitions/'

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
nut.mod <- readRDS(paste0(trans.path, 'nutrition_quality/ols/nutrition_quality_2018_2019.rds'))
```

@@

## Household Income

@@

## Pathways

### Housing Quality

```{r}
housing.base <- base %>% 
  select(pidp, time, housing_quality)

housing.energy <- energy %>% 
  select(pidp, time, housing_quality, income_boosted)

# first rename and cbind
housing.b <- rename(housing.base, base = housing_quality)
housing.e <- rename(housing.energy, energy = housing_quality)

housing.merged <- merge(housing.b, housing.e, by=c('pidp', 'time'))

housing.merged <- pivot_longer(data = housing.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'housing')

housing.merged.byyr <- housing.merged %>%
  group_by(time, scenario) %>%
  summarise(housing = mean(housing))

ggplot(data = housing.merged.byyr, mapping = aes(x = time, y = housing, color=scenario)) +
  geom_line()
```

### Neighbourhood Safety

```{r}
neighbourhood.base <- base %>% 
  select(pidp, time, neighbourhood_safety)

neighbourhood.energy <- energy %>% 
  select(pidp, time, neighbourhood_safety, income_boosted)

# first rename and cbind
neighbourhood.b <- rename(neighbourhood.base, base = neighbourhood_safety)
neighbourhood.e <- rename(neighbourhood.energy, energy = neighbourhood_safety)

neighbourhood.merged <- merge(neighbourhood.b, neighbourhood.e, by=c('pidp', 'time'))

neighbourhood.merged <- pivot_longer(data = neighbourhood.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'neighbourhood')

neighbourhood.merged.byyr <- neighbourhood.merged %>%
  group_by(time, scenario) %>%
  summarise(neighbourhood = mean(neighbourhood))

ggplot(data = neighbourhood.merged.byyr, mapping = aes(x = time, y = neighbourhood, color=scenario)) +
  geom_line()
```

### Tobacco Use

```{r}
ncigs.base <- base %>% 
  select(pidp, time, ncigs)

ncigs.energy <- energy %>% 
  select(pidp, time, ncigs, income_boosted)

# first rename and cbind
ncigs.b <- rename(ncigs.base, base = ncigs)
ncigs.e <- rename(ncigs.energy, energy = ncigs)

ncigs.merged <- merge(ncigs.b, ncigs.e, by=c('pidp', 'time'))

ncigs.merged <- pivot_longer(data = ncigs.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'ncigs')

ncigs.merged.byyr <- ncigs.merged %>%
  group_by(time, scenario) %>%
  summarise(ncigs = mean(ncigs))

ggplot(data = ncigs.merged.byyr, mapping = aes(x = time, y = ncigs, color=scenario)) +
  geom_line()
```

### Nutrition Quality

```{r}
nut.base <- base %>% 
  select(pidp, time, nutrition_quality)

nut.energy <- energy %>% 
  select(pidp, time, nutrition_quality, income_boosted)

# first rename and cbind
nut.b <- rename(nut.base, base = nutrition_quality)
nut.e <- rename(nut.energy, energy = nutrition_quality)

nut.merged <- merge(nut.b, nut.e, by=c('pidp', 'time'))

nut.merged <- pivot_longer(data = nut.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'nutrition')

nut.merged.byyr <- nut.merged %>%
  group_by(time, scenario) %>%
  summarise(nutrition = mean(nutrition))

ggplot(data = nut.merged.byyr, mapping = aes(x = time, y = nutrition, color=scenario)) +
  geom_line()
```

### Loneliness (NOT CURRENTLY IN SF12 MODEL)

```{r}
lnly.base <- base %>% 
  select(pidp, time, loneliness)

lnly.energy <- energy %>% 
  select(pidp, time, loneliness, income_boosted)

# first rename and cbind
lnly.b <- rename(lnly.base, base = loneliness)
lnly.e <- rename(lnly.energy, energy = loneliness)

lnly.merged <- merge(lnly.b, lnly.e, by=c('pidp', 'time'))

lnly.merged <- pivot_longer(data = lnly.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'loneliness')

lnly.merged.byyr <- lnly.merged %>%
  group_by(time, scenario) %>%
  summarise(loneliness = mean(loneliness))

ggplot(data = lnly.merged.byyr, mapping = aes(x = time, y = loneliness, color=scenario)) +
  geom_line()
```

@@

# END
